---
title: "Analysis Report of the EPLPA Project"
author: "Pierre-Yves de Müllenheim"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cosmo
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: yes
    df_print: paged
    code_folding: show
toc-title: "Sommaire"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{css, echo = FALSE}
.title {
  font-weight: bold;
}


h1 {
  font-size: 25px;
  font-weight: bold;
}
h2 {
  font-size: 23px;
  font-weight: bold;
}
h3 {
  font-size: 21px;
}
p.caption {
  color: #777;
  margin-top: 10px;
}
p code {
  white-space: inherit;
}
pre {
  word-break: normal;
  word-wrap: normal;
}
pre code {
  white-space: inherit;
}
```

```{r load_packages}
library(corrplot)
library(dplyr)
library(flextable)
library(forcats)
library(ggplot2)
library(ggrain)
library(Hmisc)
library(lubridate)
library(patchwork)
library(RColorBrewer)
library(scales)
library(skimr)
library(rcompanion)
library(reactable)
library(tidyr)
source("R/plot_score_distri.R")
```

```{r, load_objects}
targets::tar_load(capl_res)
targets::tar_load(pa_data)
```

# Dataset skimming

```{r skim_capl_res}
skim(capl_res)
```

# Physical literacy scores & interpretations
## Whole group of students
### Scores: Distributions (global, domain and sub-domain scores)

```{r get_plots_pc_scores}
# Select PC scores
pc_scores <-
  capl_res |>
  select(identifiant,
         pacer_score,
         camsa_score,
         plank_score,
         pc_score) |>
  pivot_longer(cols = pacer_score:pc_score,
               names_to = "Item",
               values_to = "Score") |>
  mutate(
    Item = fct_relevel(Item, "pacer_score", "camsa_score", "plank_score", "pc_score"),
    Item = fct_recode(
      Item,
      "PACER Shuttle Run (/10)" = "pacer_score",
      "CAMSA Score (/10)" = "camsa_score",
      "Plank (/10)" = "plank_score",
      "Physical Competence (/30)" = "pc_score"
    )
  ) 

# Get the numbers of students with valid data for each item
n_pc_scores <-
  pc_scores |>
  group_by(Item) |>
  summarise(n = sum(ifelse(!is.na(Score), 1, 0)))

# Get plots with score distributions
## Pacer
p_pc_1 <-
  plot_score_distri(
    data1 = pc_scores,
    data2 = n_pc_scores,
    item = "PACER Shuttle Run (/10)",
    color = "#333378",
    text_y = 0.45,
    breaks_x = seq(0, 10, 2),
    limits_x = c(0, 10)
  )

## CAMSA
p_pc_2 <-
  plot_score_distri(
    data1 = pc_scores,
    data2 = n_pc_scores,
    item = "CAMSA Score (/10)",
    color = "#333378",
    text_y = 0.45,
    breaks_x = seq(0, 10, 2),
    limits_x = c(0, 10)
  )

## Plank
p_pc_3 <-
  plot_score_distri(
    data1 = pc_scores,
    data2 = n_pc_scores,
    item = "Plank (/10)",
    color = "#333378",
    text_y = 0.45,
    breaks_x = seq(0, 10, 2),
    limits_x = c(0, 10)
  )

## PC score
p_pc_4 <-
  plot_score_distri(
    data1 = pc_scores,
    data2 = n_pc_scores,
    item = "Physical Competence (/30)",
    color = "#333378",
    text_y = 0.45,
    breaks_x = seq(0, 30, 10),
    limits_x = c(0, 30)
  )
```

```{r get_plots_db_scores}
# Select DB scores
db_scores <-
  capl_res |>
  select(identifiant,
         step_score,
         self_report_pa_score,
         db_score) |>
  pivot_longer(cols = step_score:db_score,
               names_to = "Item",
               values_to = "Score") |>
  mutate(
    Item = fct_relevel(Item, "step_score", "self_report_pa_score", "db_score"),
    Item = fct_recode(
      Item,
      "Average Daily Sept Count (/25)" = "step_score",
      "Self-Rep. Num. of Days with MVPA (/5)" = "self_report_pa_score",
      "Daily Behaviour (/30)" = "db_score"
    )
  ) 

# Get the numbers of students with valid data for each item
n_db_scores <-
  db_scores |>
  group_by(Item) |>
  summarise(n = sum(ifelse(!is.na(Score), 1, 0)))

# Get plots with score distributions
## Steps
p_db_1 <-
  plot_score_distri(
    data1 = db_scores,
    data2 = n_db_scores,
    item = "Average Daily Sept Count (/25)",
    color = "#9C8E84",
    text_y = 0.47,
    breaks_x = seq(0, 25, 5),
    limits_x = c(0, 25)
  )
  
## Self-reported PA
p_db_2 <-
  plot_score_distri(
    data1 = db_scores,
    data2 = n_db_scores,
    item = "Self-Rep. Num. of Days with MVPA (/5)",
    color = "#9C8E84",
    text_y = 0.47,
    breaks_x = seq(0, 5, 1),
    limits_x = c(0, 5)
  )

## DB score
p_db_3 <-
  plot_score_distri(
    data1 = db_scores,
    data2 = n_db_scores,
    item = "Daily Behaviour (/30)",
    color = "#9C8E84",
    text_y = 0.47,
    breaks_x = seq(0, 30, 10),
    limits_x = c(0, 30)
  )
```

```{r get_plots_mc_scores}
# Select MC scores
mc_scores <-
  capl_res |>
  select(
    identifiant,
    predilection_score,
    adequacy_score,
    intrinsic_motivation_score,
    pa_competence_score,
    mc_score
  ) |>
  pivot_longer(cols = predilection_score:mc_score,
               names_to = "Item",
               values_to = "Score") |>
  mutate(
    Item = fct_relevel(
      Item,
      "intrinsic_motivation_score",
      "pa_competence_score",
      "predilection_score",
      "adequacy_score",
      "mc_score"
    ),
    Item = fct_recode(
      Item,
      "Intrinsic Motivation (/7.5)" = "intrinsic_motivation_score",
      "Competence (/7.5)" = "pa_competence_score",
      "Predilection (/7.5)" = "predilection_score",
      "Adequacy (/7.5)" = "adequacy_score",
      "Motivation and Confidence (/30)" = "mc_score"
  )
  )

# Get the numbers of students with valid data for each item
n_mc_scores <-
  mc_scores |>
  group_by(Item) |>
  summarise(n = sum(ifelse(!is.na(Score), 1, 0)))

# Get plots with score distributions
## Intrinsic motivation
p_mc_1 <-
  plot_score_distri(
    data1 = mc_scores,
    data2 = n_mc_scores,
    item = "Intrinsic Motivation (/7.5)",
    color = "#EF6723",
    text_y = 0.45,
    breaks_x = seq(0, 7.5, 1.5),
    limits_x = c(0, 7.5)
  )

## Competence
p_mc_2 <-
  plot_score_distri(
    data1 = mc_scores,
    data2 = n_mc_scores,
    item = "Competence (/7.5)",
    color = "#EF6723",
    text_y = 0.45,
    breaks_x = seq(0, 7.5, 1.5),
    limits_x = c(0, 7.5)
  )

## Predilection
p_mc_3 <-
  plot_score_distri(
    data1 = mc_scores,
    data2 = n_mc_scores,
    item = "Predilection (/7.5)",
    color = "#EF6723",
    text_y = 0.45,
    breaks_x = seq(0, 7.5, 1.5),
    limits_x = c(0, 7.5)
  )

## Adequacy
p_mc_4 <-
  plot_score_distri(
    data1 = mc_scores,
    data2 = n_mc_scores,
    item = "Adequacy (/7.5)",
    color = "#EF6723",
    text_y = 0.45,
    breaks_x = seq(0, 7.5, 1.5),
    limits_x = c(0, 7.5)
  )

## MC score
p_mc_5 <-
  plot_score_distri(
    data1 = mc_scores,
    data2 = n_mc_scores,
    item = "Motivation and Confidence (/30)",
    color = "#EF6723",
    text_y = 0.45,
    breaks_x = seq(0, 30, 10),
    limits_x = c(0, 30)
  )
```

```{r get_plots_ku_scores}
# Select KU scores
ku_scores <-
  capl_res |>
  select(
    identifiant,
    fill_in_the_blanks_score,
    pa_guideline_score,
    crf_means_score,
    ms_means_score,
    sports_skill_score,
    ku_score
  ) |>
  pivot_longer(cols = fill_in_the_blanks_score:ku_score,
               names_to = "Item",
               values_to = "Score") |>
  mutate(
    Item = fct_relevel(
      Item,
      "fill_in_the_blanks_score",
      "pa_guideline_score",
      "crf_means_score",
      "ms_means_score",
      "sports_skill_score",
      "ku_score"
    ),
    Item = fct_recode(
      Item,
      "PA Comprehension and Understanding (/6)" = "fill_in_the_blanks_score",
      "Daily PA Guidelines (/1)" = "pa_guideline_score",
      "Cardiorerspiratory Fitness Definition (/1)" = "crf_means_score",
      "Muscular Strength & Endurance Definition (/1)" = "ms_means_score",
      "Improve Sport Skill (/1)" = "sports_skill_score",
      "Knowledge and Understanding (/10)" = "ku_score"
    )
  )

# Get the numbers of students with valid data for each item
n_ku_scores <-
  ku_scores |>
  group_by(Item) |>
  summarise(n = sum(ifelse(!is.na(Score), 1, 0)))

# Get plots with score distributions
## Physical activity comprehension and understanding
p_ku_1 <-
  plot_score_distri(
    data1 = ku_scores,
    data2 = n_ku_scores,
    item = "PA Comprehension and Understanding (/6)",
    color = "#00A79F",
    text_y = 0.45,
    breaks_x = seq(0, 6, 2),
    limits_x = c(0, 6)
  )

## Daily PA guidelines
p_ku_2 <-
  plot_score_distri(
    data1 = ku_scores,
    data2 = n_ku_scores,
    type = "disc",
    item = "Daily PA Guidelines (/1)",
    color = "#00A79F",
    breaks_x = seq(0, 1, 1),
    limits_x = c(0, 1)
  )

## Cardiorerspiratory fitness definition
p_ku_3 <-
  plot_score_distri(
    data1 = ku_scores,
    data2 = n_ku_scores,
    type = "disc",
    item = "Cardiorerspiratory Fitness Definition (/1)",
    color = "#00A79F",
    breaks_x = seq(0, 1, 1),
    limits_x = c(0, 1)
  )

## Muscular strength & endurance definition
p_ku_4 <-
  plot_score_distri(
    data1 = ku_scores,
    data2 = n_ku_scores,
    type = "disc",
    item = "Muscular Strength & Endurance Definition (/1)",
    color = "#00A79F",
    breaks_x = seq(0, 1, 1),
    limits_x = c(0, 1)
  )

## Improve sport skill
p_ku_5 <-
  plot_score_distri(
    data1 = ku_scores,
    data2 = n_ku_scores,
    type = "disc",
    item = "Improve Sport Skill (/1)",
    color = "#00A79F",
    breaks_x = seq(0, 1, 1),
    limits_x = c(0, 1)
  )

## KU score
p_ku_6 <-
  plot_score_distri(
    data1 = ku_scores,
    data2 = n_ku_scores,
    item = "Knowledge and Understanding (/10)",
    color = "#00A79F",
    text_y = 0.45,
    breaks_x = seq(0, 10, 2),
    limits_x = c(0, 10)
  )
```

```{r get_plots_capl_score}
# Select
capl_score <-
  capl_res |>
  select(
    identifiant,
    capl_score

  ) |>
  pivot_longer(cols = capl_score,
               names_to = "Item",
               values_to = "Score") |>
  mutate(Item = fct_recode(Item, "Physical Literacy (/100)" = "capl_score"))

# Get the numbers of students with valid data
n_capl_score <-
  capl_score |>
  group_by(Item) |>
  summarise(n = sum(ifelse(!is.na(Score), 1, 0)))

# Get plots with score distributions
## CAPL
p_capl <-
  plot_score_distri(
    data1 = capl_score,
    data2 = n_capl_score,
    item = "Physical Literacy (/100)",
    color = "#D4D11B",
    text_y = 0.45,
    breaks_x = seq(0, 100, 20),
    limits_x = c(0, 100)
  )
```

```{r get_whole_fig_scores}
# Build blank plot
blank_plot <-
  plot_score_distri(
    data1 = pc_scores,
    data2 = n_pc_scores,
    item = "PACER Shuttle Run (/10)",
    color = "white",
    text_y = 0.45,
    breaks_x = seq(0, 10, 2),
    limits_x = c(0, 10)
  ) +
  geom_rect(
    aes(
      xmin = -2,
      xmax = 20,
      ymin = -2,
      ymax = 100
    ),
    fill  = "white",
    color = "white"
  ) 
  
# Gather domain plots
p_pl_domains <-
  p_pc_4      + p_db_3      + p_mc_5     +  p_ku_6 +
  p_pc_1      + p_db_1      + p_mc_1     +  p_ku_1 +
  p_pc_2      + p_db_2      + p_mc_2     +  p_ku_2 +
  p_pc_3      + blank_plot  + p_mc_3     +  p_ku_3 +
  blank_plot  + blank_plot  + p_mc_4     +  p_ku_4 +
  blank_plot  + blank_plot  + blank_plot +  p_ku_5 +
  plot_layout(
    nrow = 6,
    byrow = TRUE,
    axis_titles  = "collect"
  )

# Get final figure
p_pl_all <-
  (plot_spacer() + (p_capl + labs(y = "")) + plot_spacer()) / p_pl_domains + plot_layout(heights = c(1, 6))
```

```{r, show_final_fig, fig.height = 15, fig.width = 12, out.width = '100%'}
p_pl_all
```

### Scores: Descriptive statistics (global and domain scores)

```{r, desc_stats_capl_all}
capl_res |> 
  select(pc_score, db_score, mc_score, ku_score, capl_score) |> 
  skim() |> 
  yank("numeric") |> 
  as_tibble() |> 
  rename(
    Score = skim_variable,
    `Missing values` = n_missing,
    Mean = mean,
    SD = sd, 
    Minimum = p0,
    `25th perc.` = p25,
    Median = p50,
    `75th perc.` = p75,
    Maximum = p100,
    Histogram = hist
  ) |> 
  select(-complete_rate) |>
  mutate(
    across(c(Mean:Maximum), ~round(.x, 2)),
    Score = as.factor(Score),
    Score = fct_recode(
      Score,
      "Physical Competence (/30)" = "pc_score",
      "Daily Behaviour (/30)" = "db_score",
      "Motivation and Confidence (/30)" = "mc_score",
      "Knowledge and Understanding (/10)" = "ku_score",
      "Physical Literacy (/100)" = "capl_score"
    )
  ) |>
  flextable() |>
  theme_zebra() |>
  width(width = 5)
```

### Scores: Medians and respective 95% confidence intervals (global and domain scores)

```{r median_cis_all_scores}
set.seed(123)

capl_res |>
  select(pc_score, db_score, mc_score, ku_score, capl_score) |>
  pivot_longer(
    cols = c(pc_score:capl_score),
    names_to = "score",
    values_to = "value"
  ) |>
  group_by(score) |>
  nest() |>
  mutate(stats =
           lapply(data, \(x) {
             x <- x |> filter(!is.na(value))
             
             df <- rcompanion::groupwiseMedian(
               value ~ 1,
               data = x,
               bca = TRUE,
               R = 999,
               conf = 0.95
             ) |>
               mutate(n = nrow(x))
           })) |>
  select(-data) |>
  unnest(stats) |>
  mutate(
    score = as.factor(score),
    score = fct_recode(
      score,
      "Physical Competence (/30)" = "pc_score",
      "Daily Behaviour (/30)" = "db_score",
      "Motivation and Confidence (/30)" = "mc_score",
      "Knowledge and Understanding (/10)" = "ku_score",
      "Physical Literacy (/100)" = "capl_score"
    ),
    `Median [95% CI]` = paste0(Median, " [", Bca.lower, "; ", Bca.upper, "]")
  ) |>
  rename(Score = score) |>
  select(Score, `Median [95% CI]`) |> 
  flextable() |> 
  theme_zebra() |> 
  width(width = 5)
```

### Interpretations: Distributions

```{r distri_interpretations, fig.height = 7, fig.width = 9, fig.align = "center"}
# Build plot
p_inter <-
  capl_res |>
  select(c(identifiant, ends_with("interpretation"))) |>
  pivot_longer(
    cols = c(pacer_interpretation:capl_interpretation),
    names_to = "score",
    values_to = "interpretation"
  ) |>
  mutate(
    score = as.factor(score),
    interpretation = ifelse(is.na(interpretation), "Non available", interpretation),
    interpretation = as.factor(interpretation),
    interpretation = fct_relevel(
      interpretation,
      "Non available",
      "beginning",
      "progressing",
      "achieving",
      "excelling"
    ),
    interpretation = fct_recode(
      interpretation,
      "Beginning" = "beginning",
      "Progressing" = "progressing",
      "Achieving" = "achieving",
      "Excelling" = "excelling"
    ),
    score = fct_relevel(
      score,
      "pacer_interpretation",
      "camsa_interpretation",
      "plank_interpretation",
      "pc_interpretation",
      "step_interpretation",
      "db_interpretation",
      "mc_interpretation",
      "ku_interpretation",
      "capl_interpretation"
    ),
    score = fct_recode(
      score,
      "PACER Shuttle Run" = "pacer_interpretation",
      "CAMSA Score" = "camsa_interpretation",
      "Plank" = "plank_interpretation",
      "Physical Competence" = "pc_interpretation",
      "Average Daily Step Count" = "step_interpretation",
      "Daily Behaviour" = "db_interpretation",
      "Motivation and Confidence" = "mc_interpretation",
      "Knowledge and Understanding" = "ku_interpretation",
      "Physical Literacy" = "capl_interpretation"
    )
  ) |>
  count(score, interpretation, .drop = FALSE) |>
  group_by(score) |>
  mutate(prop = round(n / sum(n) * 100, 1)) |> 
  ggplot(aes(x = interpretation, y = prop)) +
  geom_bar(stat = "identity", aes(fill = interpretation)) +
  geom_text(aes(label = paste0(prop, "%")), size = 3, vjust = -0.3) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  coord_cartesian(ylim = c(0, 100)) +
  labs(x = "", y = "%", fill = "Interpretation") +
  facet_wrap( ~ score) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
    legend.title = element_text(face = "bold"),
    strip.background = element_rect(fill = "black"),
    strip.text = element_text(color = "white", face = "bold")
    )

# Show plot
p_inter
```

## By sex
### Scores: Distributions (global, domain and sub-domain scores)

```{r get_plots_pc_scores_by_sex}
# Select PC scores
pc_scores_by_sex <-
  capl_res |>
  select(identifiant,
         gender,
         pacer_score,
         camsa_score,
         plank_score,
         pc_score) |>
  pivot_longer(cols = pacer_score:pc_score,
               names_to = "Item",
               values_to = "Score") |>
  mutate(
    Item = fct_relevel(Item, "pacer_score", "camsa_score", "plank_score", "pc_score"),
    Item = fct_recode(
      Item,
      "PACER Shuttle Run (/10)" = "pacer_score",
      "CAMSA Score (/10)" = "camsa_score",
      "Plank (/10)" = "plank_score",
      "Physical Competence (/30)" = "pc_score"
    )
  ) 

# Get the numbers of students with valid data for each item
n_pc_scores_by_sex <-
  pc_scores_by_sex |>
  group_by(gender, Item) |>
  summarise(n = sum(ifelse(!is.na(Score), 1, 0)))

# Get plots with score distributions
## Pacer
p_pc_1_by_sex  <-
  plot_score_distri(
    data1 = pc_scores_by_sex ,
    data2 = n_pc_scores_by_sex ,
    item = "PACER Shuttle Run (/10)",
    by_sex = "yes",
    color = "#333378",
    text_y = 1.55,
    breaks_x = seq(0, 10, 2),
    limits_x = c(0, 10)
  )

## CAMSA
p_pc_2_by_sex  <-
  plot_score_distri(
    data1 = pc_scores_by_sex ,
    data2 = n_pc_scores_by_sex ,
    item = "CAMSA Score (/10)",
    by_sex = "yes",
    color = "#333378",
    text_y = 1.55,
    breaks_x = seq(0, 10, 2),
    limits_x = c(0, 10)
  )

## Plank
p_pc_3_by_sex <-
  plot_score_distri(
    data1 = pc_scores_by_sex ,
    data2 = n_pc_scores_by_sex ,
    item = "Plank (/10)",
    by_sex = "yes",
    color = "#333378",
    text_y = 1.55,
    breaks_x = seq(0, 10, 2),
    limits_x = c(0, 10)
  )

## PC score
p_pc_4_by_sex  <-
  plot_score_distri(
    data1 = pc_scores_by_sex ,
    data2 = n_pc_scores_by_sex ,
    item = "Physical Competence (/30)",
    by_sex = "yes",
    color = "#333378",
    text_y = 1.55,
    breaks_x = seq(0, 30, 10),
    limits_x = c(0, 30)
  )

```

```{r get_plots_db_scores_by_sex}
# Select DB scores
db_scores_by_sex <-
  capl_res |>
  select(identifiant,
         gender,
         step_score,
         self_report_pa_score,
         db_score) |>
  pivot_longer(cols = step_score:db_score,
               names_to = "Item",
               values_to = "Score") |>
  mutate(
    Item = fct_relevel(Item, "step_score", "self_report_pa_score", "db_score"),
    Item = fct_recode(
      Item,
      "Average Daily Sept Count (/25)" = "step_score",
      "Self-Rep. Num. of Days with MVPA (/5)" = "self_report_pa_score",
      "Daily Behaviour (/30)" = "db_score"
    )
  ) 

# Get the numbers of students with valid data for each item
n_db_scores_by_sex <-
  db_scores_by_sex |>
  group_by(gender, Item) |>
  summarise(n = sum(ifelse(!is.na(Score), 1, 0)))

# Get plots with score distributions
## Steps
p_db_1_by_sex <-
  plot_score_distri(
    data1 = db_scores_by_sex,
    data2 = n_db_scores_by_sex,
    item = "Average Daily Sept Count (/25)",
    by_sex = "yes",
    color = "#9C8E84",
    text_y = 1.55,
    breaks_x = seq(0, 25, 5),
    limits_x = c(0, 25)
  )
  
## Self-reported PA
p_db_2_by_sex <-
  plot_score_distri(
    data1 = db_scores_by_sex,
    data2 = n_db_scores_by_sex,
    item = "Self-Rep. Num. of Days with MVPA (/5)",
    by_sex = "yes",
    color = "#9C8E84",
    text_y = 1.55,
    breaks_x = seq(0, 5, 1),
    limits_x = c(0, 5)
  )

## DB score
p_db_3_by_sex <-
  plot_score_distri(
    data1 = db_scores_by_sex,
    data2 = n_db_scores_by_sex,
    item = "Daily Behaviour (/30)",
    by_sex = "yes",
    color = "#9C8E84",
    text_y = 1.55,
    breaks_x = seq(0, 30, 10),
    limits_x = c(0, 30)
  )
```

```{r get_plots_mc_scores_by_sex}
# Select MC scores
mc_scores_by_sex <-
  capl_res |>
  select(
    identifiant,
    gender,
    predilection_score,
    adequacy_score,
    intrinsic_motivation_score,
    pa_competence_score,
    mc_score
  ) |>
  pivot_longer(cols = predilection_score:mc_score,
               names_to = "Item",
               values_to = "Score") |>
  mutate(
    Item = fct_relevel(
      Item,
      "intrinsic_motivation_score",
      "pa_competence_score",
      "predilection_score",
      "adequacy_score",
      "mc_score"
    ),
    Item = fct_recode(
      Item,
      "Intrinsic Motivation (/7.5)" = "intrinsic_motivation_score",
      "Competence (/7.5)" = "pa_competence_score",
      "Predilection (/7.5)" = "predilection_score",
      "Adequacy (/7.5)" = "adequacy_score",
      "Motivation and Confidence (/30)" = "mc_score"
  )
  )

# Get the numbers of students with valid data for each item
n_mc_scores_by_sex <-
  mc_scores_by_sex |>
  group_by(gender, Item) |>
  summarise(n = sum(ifelse(!is.na(Score), 1, 0)))

# Get plots with score distributions
## Intrinsic motivation
p_mc_1_by_sex <-
  plot_score_distri(
    data1 = mc_scores_by_sex,
    data2 = n_mc_scores_by_sex,
    item = "Intrinsic Motivation (/7.5)",
    by_sex = "yes",
    color = "#EF6723",
    text_y = 1.55,
    breaks_x = seq(0, 7.5, 1.5),
    limits_x = c(0, 7.5)
  )

## Competence
p_mc_2_by_sex <-
  plot_score_distri(
    data1 = mc_scores_by_sex,
    data2 = n_mc_scores_by_sex,
    item = "Competence (/7.5)",
    by_sex = "yes", 
    color = "#EF6723",
    text_y = 1.55,
    breaks_x = seq(0, 7.5, 1.5),
    limits_x = c(0, 7.5)
  )

## Predilection
p_mc_3_by_sex <-
  plot_score_distri(
    data1 = mc_scores_by_sex,
    data2 = n_mc_scores_by_sex,
    item = "Predilection (/7.5)",
    by_sex = "yes", 
    color = "#EF6723",
    text_y = 1.55,
    breaks_x = seq(0, 7.5, 1.5),
    limits_x = c(0, 7.5)
  )

## Adequacy
p_mc_4_by_sex <-
  plot_score_distri(
    data1 = mc_scores_by_sex,
    data2 = n_mc_scores_by_sex,
    item = "Adequacy (/7.5)",
    by_sex = "yes", 
    color = "#EF6723",
    text_y = 1.55,
    breaks_x = seq(0, 7.5, 1.5),
    limits_x = c(0, 7.5)
  )

## MC score
p_mc_5_by_sex <-
  plot_score_distri(
    data1 = mc_scores_by_sex,
    data2 = n_mc_scores_by_sex,
    item = "Motivation and Confidence (/30)",
    by_sex = "yes", 
    color = "#EF6723",
    text_y = 1.55,
    breaks_x = seq(0, 30, 10),
    limits_x = c(0, 30)
  )
```

```{r get_plots_ku_scores_by_sex}
# Select KU scores
ku_scores_by_sex <-
  capl_res |>
  select(
    identifiant,
    gender,
    fill_in_the_blanks_score,
    pa_guideline_score,
    crf_means_score,
    ms_means_score,
    sports_skill_score,
    ku_score
  ) |>
  pivot_longer(cols = fill_in_the_blanks_score:ku_score,
               names_to = "Item",
               values_to = "Score") |>
  mutate(
    Item = fct_relevel(
      Item,
      "fill_in_the_blanks_score",
      "pa_guideline_score",
      "crf_means_score",
      "ms_means_score",
      "sports_skill_score",
      "ku_score"
    ),
    Item = fct_recode(
      Item,
      "PA Comprehension and Understanding (/6)" = "fill_in_the_blanks_score",
      "Daily PA Guidelines (/1)" = "pa_guideline_score",
      "Cardiorerspiratory Fitness Definition (/1)" = "crf_means_score",
      "Muscular Strength & Endurance Definition (/1)" = "ms_means_score",
      "Improve Sport Skill (/1)" = "sports_skill_score",
      "Knowledge and Understanding (/10)" = "ku_score"
    )
  )

# Get the numbers of students with valid data for each item
n_ku_scores_by_sex <-
  ku_scores_by_sex |>
  group_by(gender, Item) |>
  summarise(n = sum(ifelse(!is.na(Score), 1, 0)))

# Get plots with score distributions
## Physical activity comprehension and understanding
p_ku_1_by_sex <-
  plot_score_distri(
    data1 = ku_scores_by_sex,
    data2 = n_ku_scores_by_sex,
    item = "PA Comprehension and Understanding (/6)",
    by_sex = "yes", 
    color = "#00A79F",
    text_y = 1.55,
    breaks_x = seq(0, 6, 2),
    limits_x = c(0, 6)
  )

## Daily PA guidelines
p_ku_2_by_sex <-
  plot_score_distri(
    data1 = ku_scores_by_sex,
    data2 = n_ku_scores_by_sex,
    type = "disc",
    item = "Daily PA Guidelines (/1)",
    by_sex = "yes", 
    color = "#00A79F",
    breaks_x = seq(0, 1, 1),
    limits_x = c(0, 1)
  )

## Cardiorerspiratory fitness definition
p_ku_3_by_sex <-
  plot_score_distri(
    data1 = ku_scores_by_sex,
    data2 = n_ku_scores_by_sex,
    type = "disc",
    item = "Cardiorerspiratory Fitness Definition (/1)",
    by_sex = "yes", 
    color = "#00A79F",
    breaks_x = seq(0, 1, 1),
    limits_x = c(0, 1)
  )

## Muscular strength & endurance definition
p_ku_4_by_sex <-
  plot_score_distri(
    data1 = ku_scores_by_sex,
    data2 = n_ku_scores_by_sex,
    type = "disc",
    item = "Muscular Strength & Endurance Definition (/1)",
    by_sex = "yes", 
    color = "#00A79F",
    breaks_x = seq(0, 1, 1),
    limits_x = c(0, 1)
  )

## Improve sport skill
p_ku_5_by_sex <-
  plot_score_distri(
    data1 = ku_scores_by_sex,
    data2 = n_ku_scores_by_sex,
    type = "disc",
    item = "Improve Sport Skill (/1)",
    by_sex = "yes",
    color = "#00A79F",
    breaks_x = seq(0, 1, 1),
    limits_x = c(0, 1)
  )

## KU score
p_ku_6_by_sex <-
  plot_score_distri(
    data1 = ku_scores_by_sex,
    data2 = n_ku_scores_by_sex,
    item = "Knowledge and Understanding (/10)",
    by_sex = "yes", 
    color = "#00A79F",
    text_y = 1.55,
    breaks_x = seq(0, 10, 2),
    limits_x = c(0, 10)
  )
```

```{r get_plots_capl_score_by_sex}
# Select
capl_score_by_sex <-
  capl_res |>
  select(
    identifiant,
    gender,
    capl_score

  ) |>
  pivot_longer(cols = capl_score,
               names_to = "Item",
               values_to = "Score") |>
  mutate(Item = fct_recode(Item, "Physical Literacy (/100)" = "capl_score"))

# Get the numbers of students with valid data
n_capl_score_by_sex <-
  capl_score_by_sex |>
  group_by(gender, Item) |>
  summarise(n = sum(ifelse(!is.na(Score), 1, 0)))

# Get plots with score distributions
## CAPL
p_capl_by_sex <-
  plot_score_distri(
    data1 = capl_score_by_sex,
    data2 = n_capl_score_by_sex,
    item = "Physical Literacy (/100)",
    by_sex = "yes", 
    color = "#D4D11B",
    text_y = 1.55,
    breaks_x = seq(0, 100, 20),
    limits_x = c(0, 100)
  )
```

```{r get_whole_fig_scores_by_sex}
# Build blank plot
blank_plot_by_sex <-
  plot_score_distri(
    data1 = pc_scores_by_sex,
    data2 = n_pc_scores_by_sex,
    item = "PACER Shuttle Run (/10)",
    color = "white",
    text_y = 1.555,
    breaks_x = seq(0, 10, 2),
    limits_x = c(0, 10)
  ) +
  geom_rect(
    aes(
      xmin = -2,
      xmax = 20,
      ymin = -2,
      ymax = 100
    ),
    fill  = "white",
    color = "white"
  ) 
  
# Gather domain plots
p_pl_domains_by_sex <-
  p_pc_4_by_sex      + p_db_3_by_sex      + p_mc_5_by_sex     +  p_ku_6_by_sex +
  p_pc_1_by_sex      + p_db_1_by_sex      + p_mc_1_by_sex     +  p_ku_1_by_sex +
  p_pc_2_by_sex      + p_db_2_by_sex     + p_mc_2_by_sex     +  p_ku_2_by_sex +
  p_pc_3_by_sex      + blank_plot_by_sex  + p_mc_3_by_sex     +  p_ku_3_by_sex +
  blank_plot_by_sex  + blank_plot_by_sex  + p_mc_4_by_sex     +  p_ku_4_by_sex +
  blank_plot_by_sex  + blank_plot_by_sex  + blank_plot_by_sex +  p_ku_5_by_sex +
  plot_layout(
    nrow = 6,
    byrow = TRUE,
    axis_titles  = "collect"
  )

# Get final figure
p_pl_by_sex <-
  (plot_spacer() + (p_capl_by_sex + labs(y = "")) + plot_spacer()) / p_pl_domains_by_sex + plot_layout(heights = c(1, 6), guides = 'collect')
```

```{r, show_final_fig_by_sex, fig.height = 15, fig.width = 13, out.width = '100%'}
p_pl_by_sex
```

### Scores: Descriptive statistics (global and domain scores)

```{r, desc_stats_capl_by_sex}
capl_res |> 
  select(gender, pc_score, db_score, mc_score, ku_score, capl_score) |> 
  group_by(gender) |> 
  skim() |> 
  yank("numeric") |> 
  as_tibble() |> 
  rename(
    Score = skim_variable,
    Sex = gender, 
    `Missing values` = n_missing,
    Mean = mean,
    SD = sd, 
    Minimum = p0,
    `25th perc.` = p25,
    Median = p50,
    `75th perc.` = p75,
    Maximum = p100,
    Histogram = hist
  ) |> 
  select(-complete_rate) |>
  mutate(
    across(c(Mean:Maximum), ~round(.x, 2)),
    Score = as.factor(Score),
    Score = fct_recode(
      Score,
      "Physical Competence (/30)" = "pc_score",
      "Daily Behaviour (/30)" = "db_score",
      "Motivation and Confidence (/30)" = "mc_score",
      "Knowledge and Understanding (/10)" = "ku_score",
      "Physical Literacy (/100)" = "capl_score"
    ),
    Sex = fct_recode(
      Sex, "Girl" = "girl", "Boy" = "boy"
    )
  ) |>
  flextable() |>
  theme_zebra() |>
  width(width = 5) |> 
  merge_v(j = "Score")
```

### Scores: Medians and respective 95% confidence intervals (global and domain scores)

```{r median_cis_all_scores_by_sex}
set.seed(123)

capl_res |>
  select(gender, pc_score, db_score, mc_score, ku_score, capl_score) |>
  pivot_longer(
    cols = c(pc_score:capl_score),
    names_to = "score",
    values_to = "value"
  ) |>
  group_by(score) |>
  nest() |>
  mutate(stats =
           lapply(data, \(x) {
             x <- x |> filter(!is.na(value))
             
             df <- rcompanion::groupwiseMedian(
               value ~ gender,
               data = x,
               bca = TRUE,
               R = 999,
               conf = 0.95
             ) |>
               mutate(n = nrow(x))
           })) |>
  select(-data) |>
  unnest(stats) |>
  mutate(
    score = as.factor(score),
    score = fct_recode(
      score,
      "Physical Competence (/30)" = "pc_score",
      "Daily Behaviour (/30)" = "db_score",
      "Motivation and Confidence (/30)" = "mc_score",
      "Knowledge and Understanding (/10)" = "ku_score",
      "Physical Literacy (/100)" = "capl_score"
    ),
    gender = fct_recode(gender, "Girl" = "girl", "Boy" = "boy"),
    `Median [95% CI]` = paste0(Median, " [", Bca.lower, "; ", Bca.upper, "]")
  ) |>
  rename(Score = score, Sex = gender) |>
  select(Score, Sex, `Median [95% CI]`) |>
  flextable() |>
  theme_zebra() |>
  width(width = 5) |> 
  merge_v(j = "Score")
```

### Interpretations: Distributions

```{r distri_interpretations_by_sex, fig.height = 7, fig.width = 9, fig.align = "center"}
# Build plot
p_inter_by_sex <-
  capl_res |>
  select(c(identifiant, gender, ends_with("interpretation"))) |>
  pivot_longer(
    cols = c(pacer_interpretation:capl_interpretation),
    names_to = "score",
    values_to = "interpretation"
  ) |>
  mutate(
    score = as.factor(score),
    interpretation = ifelse(is.na(interpretation), "Non available", interpretation),
    interpretation = as.factor(interpretation),
    interpretation = fct_relevel(
      interpretation,
      "Non available",
      "beginning",
      "progressing",
      "achieving",
      "excelling"
    ),
    interpretation = fct_recode(
      interpretation,
      "Beginning" = "beginning",
      "Progressing" = "progressing",
      "Achieving" = "achieving",
      "Excelling" = "excelling"
    ),
    score = fct_relevel(
      score,
      "pacer_interpretation",
      "camsa_interpretation",
      "plank_interpretation",
      "pc_interpretation",
      "step_interpretation",
      "db_interpretation",
      "mc_interpretation",
      "ku_interpretation",
      "capl_interpretation"
    ),
    score = fct_recode(
      score,
      "PACER Shuttle Run" = "pacer_interpretation",
      "CAMSA Score" = "camsa_interpretation",
      "Plank" = "plank_interpretation",
      "Physical Competence" = "pc_interpretation",
      "Average Daily Step Count" = "step_interpretation",
      "Daily Behaviour" = "db_interpretation",
      "Motivation and Confidence" = "mc_interpretation",
      "Knowledge and Understanding" = "ku_interpretation",
      "Physical Literacy" = "capl_interpretation"
    )
  ) |>
  count(gender, score, interpretation, .drop = FALSE) |>
  group_by(gender, score) |>
  mutate(prop = round(n / sum(n) * 100, 0)) |> 
  ggplot(aes(x = interpretation, y = prop)) +
  geom_bar(stat = "identity", aes(fill = gender), position = position_dodge(width = 0.9)) +
  geom_text(aes(label = paste0(prop, "%"), group = gender), position = position_dodge(width = 0.9), size = 2, vjust = -0.3) +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  scale_fill_manual(values = c("hotpink", "royalblue2"), labels = c("Girl", "Boy")) +
  coord_cartesian(ylim = c(0, 100)) +
  labs(x = "", y = "%", fill = "Sex") +
  facet_wrap( ~ score) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
    legend.title = element_text(face = "bold"),
    strip.background = element_rect(fill = "black"),
    strip.text = element_text(color = "white", face = "bold")
    )

# Show plot
p_inter_by_sex
```

# Relationships between the physical literacy scores (global and domain scores)

```{r get_corr_matrix_capl, results = "hide", fig.keep = "none"}
# Rename variables and keep only the subjects with complete observations for
# all variables
df_corr_capl <-
  capl_res |> 
  select(pc_score, db_score, mc_score, ku_score, capl_score) |> 
  rename(
    "Physical Competence" = pc_score,
    "Daily Behaviour" = db_score,
    "Motivation and Confidence" = mc_score,
    "Knowledge & Understanding" = ku_score,
    "Physical Literacy" = capl_score
  ) |> 
  drop_na()

# Get matrix of correlations
mat_corr_capl  <- cor(df_corr_capl, method = "spearman")

# Get matrix of p-values
mat_corr_p_capl <- (cor.mtest(df_corr_capl, method = "spearman"))$p

# Get corrplot infos
corrplot_capl_infos <- 
  corrplot(
    mat_corr_capl,
    order = 'hclust',
    method = "color",
    tl.col = "black",
    addCoef.col = "black",
    mar = c(0, 0, 0, 0),
    tl.srt = 45,
    tl.cex = 0.6,
    number.cex = 0.5,
    col = COL2('PuOr', 10),
    p.mat = mat_corr_p_capl,
    sig.level = 0.05
  )
```

```{r build_plot_corr_matrix_capl}
p_corr_capl <-
  ggplot(corrplot_capl_infos$corrPos, aes(x = x, y = y)) +
  geom_tile(aes(fill = corr), color = "grey90") +
  geom_text(
    aes(label = round(corr, 2)),
    size = 4,
    color = ifelse(corrplot_capl_infos$corrPos$corr == 1, NA,
      ifelse(corrplot_capl_infos$corrPos$p.value <= 0.05, "black","grey30"))
  ) +
    geom_text(
    aes(y = y - 0.25, label = ifelse(p.value <= 0.001, "(p<=0.001)", paste0("(p=", format(round(p.value, 3), nsmall = 3), ")"))),
    size = 2,
    color = ifelse(corrplot_capl_infos$corrPos$corr == 1, NA,
      ifelse(corrplot_capl_infos$corrPos$p.value <= 0.05, "black","grey30"))
  ) +
  geom_text(
    aes(y = 0.2, label = xName),
    angle = 90,
    hjust = 1,
    vjust = 0.5,
    size = 3
  ) +
  geom_text(aes(x = 0.3, label = yName), hjust = 1, size = 3) +
  scale_fill_gradient2(
    low = "red",
    high = "blue",
    mid = "white",
    midpoint = 0,
    breaks = seq(-1, 1, 0.2),
    limits = c(-1, 1)
  ) +
  guides(fill = guide_legend(title = NULL, reverse = TRUE)) +
  theme_classic() +
  coord_cartesian(xlim = c(-1.65, 6), ylim = c(-1.65, 6)) +
  theme(
    legend.position = c(0.955, 0.6),
    legend.spacing.x = unit(0, 'cm'),
    legend.key.size = unit(0.6,"line"),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    axis.ticks = element_blank()
    ) 
```

The matrix of correlations shown below is based on `r nrow(df_corr_capl)` students with complete data. Values are Spearman rho correlation coefficients.

```{r show_plot_corr_matrix_capl, fig.align = "center", out.width = '80%', fig.width = 6, fig.height = 6}
p_corr_capl
```

# Physical behaviour metrics (using students with \>=4 valid days)
## Whole group of students
### Metrics: Descriptive statistics

The power low exponent alpha coefficient, the median bout duration, the usual bout duration, and the Gini index are computed using the week as a whole. All the other metrics represent daily averages.

```{r pa_data_selection}
pa_data_select <-
  pa_data$all_metrics |>
  filter(valid_days >= 4)
```

```{r pa_metrics_desc}
pa_data_select |>
  select(-c(id, total_kcal, pal)) |>
  skim() |>
  yank("numeric") |>
  as_tibble() |>
  rename(
    Metric = skim_variable,
    `Missing values` = n_missing,
    Mean = mean,
    SD = sd,
    Minimum = p0,
    `25th perc.` = p25,
    Median = p50,
    `75th perc.` = p75,
    Maximum = p100,
    Histogram = hist
  ) |>
  select(-complete_rate) |>
  mutate(
    across(c(Mean:Maximum), ~ round(.x, 2)),
    Metric = as.factor(Metric),
    Metric = fct_recode(Metric,
      "Num. of valid days" = "valid_days",
      "Wear time (min)" = "wear_time",
      "VA total counts" = "total_counts_axis1",
      "VM total counts" = "total_counts_vm",
      "VA counts/min" = "axis1_per_min",
      "VM counts/min" = "vm_per_min",
      "SED time (min)" = "minutes_SED",
      "LPA time (min)" = "minutes_LPA",
      "MPA time (min)" = "minutes_MPA",
      "VPA time (min)" = "minutes_VPA",
      "MVPA time (min)" = "minutes_MVPA",
      "% Wear time SED" = "percent_SED",
      "% Wear time LPA" = "percent_LPA",
      "% Wear time MPA" = "percent_MPA",
      "% Wear time VPA" = "percent_VPA",
      "% Wear time MVPA" = "percent_MVPA",
      "Ratio MVPA / SED" = "ratio_mvpa_sed",
      "MVPA MET-hr" = "mets_hours_mvpa",
      "Total steps" = "total_steps",
      "Max steps accum. / min over 60 min" = "max_steps_60min",
      "Max steps accum. / min over 30 min" = "max_steps_30min",
      "Max steps accum. / min over 20 min" = "max_steps_20min",
      "Max steps accum. / min over 5 min" = "max_steps_5min",
      "Max steps accum. / min over 1 min" = "max_steps_1min",
      "Peak steps accum. / min over 60 min" = "peak_steps_60min",
      "Peak steps accum. / min over 30 min" = "peak_steps_30min",
      "Peak steps accum. / min over 20 min" = "peak_steps_20min",
      "Peak steps accum. / min over 5 min" = "peak_steps_5min",
      "Peak steps accum. / min over 1 min" = "peak_steps_1min",
      "Intensity gradient" = "ig",
      "Min. of counts/epoch over the best 8 hrs" = "M1/3",
      "Min. of counts/epoch over the best 120 min" = "M120",
      "Min. of counts/epoch over the best 60 min" = "M60",
      "Min. of counts/epoch over the best 30 min" = "M30",
      "Min. of counts/epoch over the best 15 min" = "M15",
      "Min. of counts/epoch over the best 5 min" = "M5",
      "Number of breaks" = "mean_breaks",
      "Power low exponent alpha" = "alpha",
      "Median bout duration (min)" = "MBD",
      "Usual bout duration (min)" = "UBD",
      "Gini index" = "gini"
    )
  ) |>
  reactable(
    defaultColDef = colDef(
      minWidth = 95,
      headerStyle = list(background = "#f7f7f8")
    ),
    columns = list(Metric = colDef(
      sticky = "left",
      style = list(borderRight = "1px solid #eee"),
      headerStyle = list(borderRight = "1px solid #eee", background = "#f7f7f8"),
      minWidth = 170
    )
  ),
highlight = TRUE, bordered = TRUE
)
```

# Relationships between the global physical literacy scores and the physical behaviour metrics

```{r get_corr_matrix_pa, results = "hide", fig.keep = "none"}
# Rename variables and keep only the subjects with complete observations for
# all variables
df_corr_pa <-
  pa_data_select |>
  rename(identifiant = id) |>
  mutate(identifiant = as.factor(identifiant)) |>
  left_join(capl_res |> select(c(-valid_days)), by = "identifiant") |>
  select(wear_time:gini,
         -minutes_VPA,
         -percent_VPA,
         -total_kcal,
         -pal,
         -mets_hours_mvpa,
         pc_score,
         db_score,
         mc_score,
         ku_score,
         capl_score)  |>
  drop_na() |> 
  rename(
      "Daily Wear time (min)" = "wear_time",
      "Daily VA total counts" = "total_counts_axis1",
      "Daily VM total counts" = "total_counts_vm",
      "Daily VA counts/min" = "axis1_per_min",
      "Daily VM counts/min" = "vm_per_min",
      "Daily SED time (min)" = "minutes_SED",
      "Daily LPA time (min)" = "minutes_LPA",
      "Daily MPA time (min)" = "minutes_MPA",
      "Daily MVPA time (min)" = "minutes_MVPA",
      "Daily % Wear time SED" = "percent_SED",
      "Daily % Wear time LPA" = "percent_LPA",
      "Daily % Wear time MPA" = "percent_MPA",
      "Daily % Wear time MVPA" = "percent_MVPA",
      "Daily Ratio MVPA / SED" = "ratio_mvpa_sed",
      "Daily Total steps" = "total_steps",
      "Daily Max steps accum. 60 min" = "max_steps_60min",
      "Daily Max steps accum. 30 min" = "max_steps_30min",
      "Daily Max steps accum. 20 min" = "max_steps_20min",
      "Daily Max steps accum. 5 min" = "max_steps_5min",
      "Daily Max steps accum. 1 min" = "max_steps_1min",
      "Daily Peak steps accum. 60 min" = "peak_steps_60min",
      "Daily Peak steps accum. 30 min" = "peak_steps_30min",
      "Daily Peak steps accum. 20 min" = "peak_steps_20min",
      "Daily Peak steps accum. 5 min" = "peak_steps_5min",
      "Daily Peak steps accum. 1 min" = "peak_steps_1min",
      "Daily Intensity gradient" = "ig",
      "Daily MX 8hrs" = "M1/3",
      "Daily MX 120 min" = "M120",
      "Daily MX 60 min" = "M60",
      "Daily MX 30 min" = "M30",
      "Daily MX 15 min" = "M15",
      "Daily MX 5" = "M5",
      "Daily Number of breaks" = "mean_breaks",
      "Power low exponent alpha" = "alpha",
      "Median bout duration (min)" = "MBD",
      "Usual bout duration (min)" = "UBD",
      "Gini index" = "gini",
      "Physical Competence" = pc_score,
      "Daily Behaviour" = db_score,
      "Motivation and Confidence" = mc_score,
      "Knowledge & Understanding" = ku_score,
      "Physical Literacy" = capl_score

  )

# Get matrix of correlations
mat_corr_pa  <- cor(df_corr_pa, method = "spearman")

# Get matrix of p-values
mat_corr_p_pa <- (cor.mtest(df_corr_pa, method = "spearman"))$p

# Get corrplot infos
corrplot_pa_infos <- 
  corrplot(
    mat_corr_pa,
    order = 'hclust',
    method = "color",
    tl.col = "black",
    addCoef.col = "black",
    mar = c(0, 0, 0, 0),
    tl.srt = 45,
    tl.cex = 0.6,
    number.cex = 0.5,
    col = COL2('PuOr', 10),
    p.mat = mat_corr_p_pa,
    sig.level = 0.05
  )
```

```{r build_plot_corr_matrix_pa}
p_corr_pa <-
  ggplot(corrplot_pa_infos$corrPos, aes(x = x, y = y)) +
  geom_tile(aes(fill = corr), color = "grey90") +
  geom_text(
    aes(label = round(corr, 2)),
    size = 2.6,
    color = ifelse(corrplot_pa_infos$corrPos$corr == 1, NA,
      ifelse(corrplot_pa_infos$corrPos$p.value <= 0.05, "black","grey30"))
  ) +
    geom_text(
    aes(y = y - 0.25, label = ifelse(p.value <= 0.001, "(p<=0.001)", paste0("(p=", format(round(p.value, 3), nsmall = 3), ")"))),
    size = 1,
    color = ifelse(corrplot_pa_infos$corrPos$corr == 1, NA,
      ifelse(corrplot_pa_infos$corrPos$p.value <= 0.05, "black","grey30"))
  ) +
  geom_text(
    aes(y = 0.2, label = xName),
    angle = 90,
    hjust = 1,
    vjust = 0.5,
    size = 3
  ) +
  geom_text(aes(x = 0.3, label = yName), hjust = 1, size = 3) +
  scale_fill_gradient2(
    low = "red",
    high = "blue",
    mid = "white",
    midpoint = 0,
    breaks = seq(-1, 1, 0.2),
    limits = c(-1, 1)
  ) +
  guides(fill = guide_legend(title = NULL, reverse = TRUE)) +
  theme_classic() +
  coord_cartesian(xlim = c(-4, 44), ylim = c(-4, 42)) +
  theme(
    legend.position = c(0.955, 0.6),
    legend.spacing.x = unit(0, 'cm'),
    legend.key.size = unit(0.6,"line"),
    axis.line = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    axis.ticks = element_blank()
    ) 
```

The matrix of correlations shown below is based on `r nrow(df_corr_pa)` students with complete data. Values are Spearman rho correlation coefficients.

```{r show_plot_corr_matrix_pa, fig.align = "center", out.width = '100%', fig.width = 14, fig.height = 14}
p_corr_pa
```

# Patterns of steps during the days of the week for the students with at least 4 valid days
## Patterns for all students as a whole

```{r get_pa_pattern_all, fig = "center", out.width = '100%'}
# Get the IDs of the students
ids_pa_valid <-
  pa_data$all_metrics |> 
  filter(valid_days >= 4) |> 
  pull(id) 

# Get a dataset of total steps per hour for each student and day
step_per_hour <-
  pa_data$data_with_intensity_marks |>
  filter(id %in% ids_pa_valid) |>
  mutate(hour = hour(time)) |>
  mutate(
    weekday = fct_relevel(
      weekday,
      "lundi",
      "mardi",
      "mercredi",
      "jeudi",
      "vendredi",
      "samedi",
      "dimanche"
    )
  ) |>
  group_by(id, weekday, hour) |>
  summarise(tot_steps = sum(steps))

# Get statistics summaries
step_per_hour_stats <- 
  step_per_hour |> 
  group_by(weekday, hour) |> 
  summarise(
    mean = mean(tot_steps),
    sd = sd(tot_steps)
    ) |> 
  mutate(
    lower_bound = mean - sd,
    upper_bound = mean + sd
  )

# Plot data
ggplot(data = step_per_hour) +
  geom_point(aes(x = hour, y = tot_steps), alpha = 0.3, size = 1) +
  geom_ribbon(data = step_per_hour_stats, 
            aes(x = hour, ymin = lower_bound, ymax = upper_bound, fill = "Mean ± SD"),
            alpha = 0.3
            ) +
  geom_point(data = step_per_hour_stats, aes(x = hour, y = mean, color = "Mean ± SD"), size = 2) +
  geom_line(data = step_per_hour_stats, aes(x = hour, y = mean, color = "Mean ± SD"), linewidth = 0.5) +
 scale_x_continuous(breaks = seq(0, 24, 2)) +
  scale_color_manual(name ="", values = c("black", "black")) +
  scale_fill_manual(name ="", values = "blue") +
  labs(x = "Hour of the day", y = "Total number of steps") + 
  facet_wrap(~ weekday) +
  theme(legend.position = "bottom")
```

## Patterns for the students according to the quartiles

```{r get_pa_pattern_quart, fig = "center", out.width = '100%'}
# Get the quantiles for total steps
quant <- 
  pa_data$all_metrics |>
  filter(valid_days >= 4) |>
  summarise_at(vars(total_steps), list(
    Q1 =  ~ quantile(., probs = 0.25),
    median = median,
    Q3 =  ~ quantile(., probs = 0.75)
  )
  )

# Bind the IDs and Quartiles of the students with their data
step_per_hour_quart <-
  pa_data$all_metrics |> 
  filter(valid_days >= 4) |> 
  mutate(Quartile = case_when(
    total_steps <= quant$Q1 ~ "Q1",
    total_steps > quant$Q1 & total_steps <= quant$median  ~ "Q2",
    total_steps > quant$median & total_steps <= quant$Q3  ~ "Q3",
    total_steps > quant$Q3 ~ "Q4"
  )) |> 
  select(id, Quartile) |> 
  left_join(step_per_hour)

# Get statistics summaries
step_per_hour_quart_stats <- 
  step_per_hour_quart |> 
  group_by(Quartile, weekday, hour) |> 
  summarise(
    mean = mean(tot_steps),
    sd = sd(tot_steps)
    ) |> 
  mutate(
    lower_bound = mean - sd,
    upper_bound = mean + sd
  )

# Plot data
ggplot(data = step_per_hour_quart) +
  geom_point(aes(x = hour, y = tot_steps, color = Quartile), alpha = 0.3, size = 1) +
  #geom_ribbon(data = step_per_hour_quart_stats, 
            #aes(x = hour, ymin = lower_bound, ymax = upper_bound, fill = Quartile),
            #alpha = 0.3
            #) +
  geom_point(data = step_per_hour_quart_stats, aes(x = hour, y = mean, color = Quartile), size = 2) +
  geom_line(data = step_per_hour_quart_stats, aes(x = hour, y = mean, color = Quartile), linewidth = 0.5) +
 scale_x_continuous(breaks = seq(0, 24, 2)) +
  labs(x = "Hour of the day", y = "Total number of steps", color = "Mean") + 
  facet_wrap(~ weekday) +
  theme(legend.position = "bottom")
```

```{r export_results, include = FALSE}
# Export PA metrics
write_csv2(pa_data$all_metrics, "out/pa_all_metrics.csv")

# Export PA results by day
write_csv2(pa_data$results_by_day, "out/pa_results_by_day.csv")

# Export PA marked data
write_csv2(pa_data$data_with_intensity_marks, "out/pa_data_with_intensity_marks.csv")

# Export CAPL results
write_csv2(capl_res, "out/capl_results.csv")
```

```{r export_figures}
ggsave("out/pl_all.png", p_pl_all, height = 20, width = 15, unit = "cm", dpi = 300, scale = 2)
ggsave("out/pl_by_sex.png", p_pl_by_sex, height = 20, width = 16, unit = "cm", dpi = 300, scale = 2)
ggsave("out/inter.png", p_inter, height = 8, width = 11, unit = "cm", dpi = 300, scale = 2)
ggsave("out/inter_by_sex.png", p_inter_by_sex, height = 8, width = 11, unit = "cm", dpi = 300, scale = 2)
ggsave("out/corr_capl.png", p_corr_capl, height = 7, width = 7, unit = "cm", dpi = 300, scale = 2.6)
ggsave("out/corr_pa.png", p_corr_pa, height = 12, width = 12, unit = "cm", dpi = 300, scale = 3)

```
