---
title: "Comparing physical literacy scores by sex and movement behaviours across physical literacy profiles in French elementary school students (10- to 11-years old): an exploratory study from the ‘EPLPA’ project"
authors:
  - name: Henri Moncanis
    affiliation: 
      - ref: ifepsa_etud
    corresponding: false
  - name: Pierre-Yves de Müllenheim
    orcid: 0000-0001-9157-7371
    affiliation: 
      - ref: ifepsa_pro
    email: pydemull@uco.fr
    corresponding: false
  - name: Nicolas Hauw
    affiliation: 
      - ref: ifepsa_pro
    country: France
    email: nhauw@uco.fr
    corresponding: true
affiliations:
  - id: ifepsa_etud
    name: UCO-IFEPSA | Student
    city: Les Ponts-de-Cé
    country: France
  - id: ifepsa_pro
    name: UCO-IFEPSA | APCoSS
    city: Les Ponts-de-Cé
    country: France
date: today
date-format: "long"
format:
  html:
    embed-resources: true
    code-fold: true
    theme: cosmo
    toc: true
    toc-depth: 7
    toc-location: right
    number-depth: 7
    number-sections: true
    self-contained: true
    css: styles.css
title-block-banner: true
execute: 
  warning: false
  freeze: true
editor: source
---

```{r load_packages_and_targets}
#| echo: false

# Packages
library(flextable)
library(ggplot2)
library(targets)

# Targets
tar_load(tab_pa_metrics_config)
tar_load(tab_percents_num_valid_days)
tar_load(prop_4_valid_days)
tar_load(capl_res)
tar_load(p_capl_all_domains)
tar_load(desc_stats_capl_all)
tar_load(p_interpretation)
tar_load(p_capl_all_domains_by_sex)
tar_load(desc_stats_capl_by_sex)
tar_load(p_interpretation_by_sex)
tar_load(capl_comp_sex)
tar_load(p_multiv_comp_sex_dom)
tar_load(domain_global_multicomp_sex)
tar_load(domain_global_multicomp_sex_rel_eff)
tar_load(domain_local_multicomp_sex)
tar_load(domain_local_multicomp_sex_graph)
tar_load(p_multiv_comp_sex_item)
tar_load(item_global_multicomp_sex)
tar_load(item_global_multicomp_sex_rel_eff)
tar_load(item_local_multicomp_sex)
tar_load(item_local_multicomp_sex_graph)
tar_load(capl_res_4_valid_days)
tar_load(p_distri_all_metrics)
tar_load(p_biplot_metrics)
tar_load(check_cor_metrics)
tar_load(p_distri_all_metrics_by_profile)
tar_load(selected_metrics)
tar_load(tbl_retained_metrics)
tar_load(metrics_global_multicomp_profile)
tar_load(metrics_global_multicomp_profile_rel_eff)
tar_load(metrics_local_multicomp_profile)
tar_load(metrics_local_multicomp_profile_graph)
```

:::{.callout-note}
This document presents the results of the analytical pipeline of the 'EPLPA' project. If you want to look at the code that has been implemented to get the results, please see the `target.R` file and the `R/` folder associated to the present work.
:::

## Pre-analysis information

The document shows results related to CAPL-2 scores and movement behaviour metrics. CAPL-2 scores are partly based on scores related to mean daily step counts. All movement behaviour metrics (including mean daily step count) were obtained using a week-based measurement with a wGT3X-BT accelerometer (ActiGraph). The settings that have been used to process the accelerometer data files are shown in the table below. The `EPOCH_TARGET_CHILD` setting (epoch duration with which counts have been accumulated) is in seconds. The cut-points settings (intensity thresholds to perform intensity classification) are in counts/min. The `FRAME_CHILD`, `ALLOWANCE_FRAME_CHILD` and `STREAM_FRAME_CHILD` settings (to detect nonwear time) are in minutes. The `MINIMUM_WEAR_TIME` setting (to consider a day as valid for further analysis) is in hours.

```{r show_pa_metrics_config}
rmarkdown::paged_table(tab_pa_metrics_config, options = list(rows.print = 11))
```

The package used to compute CAPL-2 scores (i.e., `{capl}`) required at least 4 valid days of movement behaviour measurement to compute a mean daily step count to be used for further analysis. If only 3 valid days were available, a step count for a fourth valid day was obtained by randomly sampling a step count among the available valid daily step counts (action performed by the package `{capl}`). No computations were performed when less than 3 valid days were available.

For a better understanding of the results, the table below shows the percentages of participants by number of valid days for the measurement of movement behaviours. The percentage of participants with at least 4 valid days was `r prop_4_valid_days`%.

```{r tab_percents_num_valid_days}
#| ft.align: "center"

tab_percents_num_valid_days
```

## Global descriptive analysis of the CAPL-2 scores

This part of the document proposes a detailed view of the CAPL-2 scores obtained as results from the tests and measurements implemented during the 'EPLPA' project. Its purpose is only descriptive.

### Data skimming

#### Raw data

Navigation in the raw data is possible through the interactive table shown below. 

```{r show_capl_database}
rmarkdown::paged_table(capl_res)
```

#### Variable summaries

This section proposes an overview of the final study dataset related to the CAPL-2 scores. More precisely, the tables display information about the dataset structure as well as descriptive statistics for all the variables from the dataset. The interest of this section is mainly to verify that all the variables have been correctly formated and to have information about potential missing values.

```{r skim_capl_res}
skimr::skim(capl_res)
```

### Score distributions

This section proposes graphical and numeric summaries of the CAPL-2 scores.

#### Graphical view

```{r show_capl_scores}
#| fig.height: 15
#| fig.width: 12
#| out.width: '100%'
#| fig.align: "center"

p_capl_all_domains
```

#### Tabular view

```{r desc_stats_capl_all}
desc_stats_capl_all |>
  gtsummary::as_flex_table() |>
  italic(i = 1, j = 2, part = "header") |>
  bold(i = c(1, 5, 8, 13, 19), j = 1:3)
```

### Interpretation category distributions

This section focuses only on the counts and percentages of participants associated to the different levels of interpretation (profile) provided by the CAPL-2 tool.

```{r show_interpretations}
#| fig.height: 7
#| fig.width: 9
#| out.width: '100%'
#| fig.align: "center"

p_interpretation
```

## Between-sex comparisons of CAPL-2 scores

This part of the document proposes a detailed view of the CAPL-2 scores by sex. It has both a descriptive and an inferential purpose. 

### Score distributions

This section proposes graphical and numeric summaries of the CAPL-2 scores by sex.

#### Graphical view

```{r show_capl_scores_by_sex}
#| fig.height: 16
#| fig.width: 13
#| out.width: '100%'
#| fig.align: "center"

p_capl_all_domains_by_sex
```

#### Tabular view

```{r desc_stats_capl_by_sex}
desc_stats_capl_by_sex |>
  gtsummary::as_flex_table() |>
  bold(i = c(1, 5, 8, 13, 19), j = 1:4)
```

### Interpretation category distributions

This section focuses only on the counts and percentages of participants by sex associated to the different levels of interpretation (profile) provided by the CAPL-2 tool.

```{r show_interpretations_by_sex}
#| fig.height: 7
#| fig.width: 9
#| out.width: '100%'
#| fig.align: "center"

p_interpretation_by_sex
```

### Comparison of CAPL-2 global scores

The global comparison has been performed using a Brunner-Munzel test, that is a procedure testing the stochastic equality of the compared groups.

```{r capl_comp_sex}
capl_comp_sex
```

### Comparison of CAPL-2 domain scores

#### Graphical analysis

```{r p_multiv_comp_sex_dom}
#| fig.height: 4
#| fig.width: 9
#| out.width: '100%'
#| fig.align: "center"

p_multiv_comp_sex_dom
```

#### Checking for multivariate outliers

```{r check_outliers_domain_scores}
performance::check_outliers(
  capl_res |> 
    dplyr::select(
      pc_score, 
      db_score, 
      mc_score, 
      ku_score
      ) |> 
    tidyr::drop_na(), 
  method = "mcd") # recommended in DOI: 10.3758/s13428-024-02356-w
```

#### Non-parametric multivariate analysis

The comparison of the multivariate distributions of domain scores between girls and boys has been performed using non-parametric analysis implemented in functions from the `{npmv}` package.

##### R output for global comparison
###### Raw output

```{r domain_global_multicomp_sex}
domain_global_multicomp_sex
```

###### Formated output

```{r domain_global_multicomp_sex_rel_eff}
domain_global_multicomp_sex_rel_eff |>
  flextable() |>
  bold(i = 1, part = "header") |>
  bold( ~ `Rel. Eff. Girls` > 0.5, 4) |>
  bold( ~ `Rel. Eff. Boys` > 0.5, 5) |>
  bg( ~ `Rel. Eff. Girls` > 0.5, 4, bg = "grey90") |>
  bg( ~ `Rel. Eff. Boys` > 0.5, 5, bg = "grey90") |>
  width(j = 1, width = 2.5) |>
  width(j = 2, width = 1.5) |>
  width(j = 3, width = 1.5) |>
  valign(
    i = 1,
    j = 1:5,
    valign = "top",
    part = "header"
  ) |>
  align(j = 4:5, part = "header", align = "center") |>
  align(j = 4:5, part = "body", align = "center") |>
  add_footer_lines(
    "Min./ Max. Theo. Rel. Eff. = Minimum/maximum theoretical relative effect. A relative effect can be only between 0 and 1 and depicts the probability, for an individual randomly sampled from the considered group, to have a higher value than the one from an individual randomly sampled from both groups (girls and boys). Minimum and maximum theoretical relative effects are respectively the lowest and highest effect sizes than could be expected for a given group and score based on the number of girls and boys available for the considered score. Grey cells with bold values highlight the highest relative effects among girls and boys."
  )
```

:::{.callout-note}
The global analysis, based on the ANOVA type test p-value, suggests that girls and boys come from two different multivariate distributions related to the CAPL-2 domain scores. The `$twogroupreleffects` section of the R output shows the probability, for a given  variable, that a girl or a boy randomly sampled respectively from girls or boys has a higher value than the one associated to a participant randomly sampled from both the girls and boys.
:::

##### R output for local comparisons

###### Raw output

```{r domain_local_multicomp_sex}
cat(domain_local_multicomp_sex, sep = "\n")
```

###### Graphical output

```{r domain_local_multicomp_sex_graph}
#| fig-align: 'center'
domain_local_multicomp_sex_graph
```

### Comparison of CAPL-2 item scores

#### Graphical analysis

```{r p_multiv_comp_sex_item}
#| fig.height: 12
#| fig.width: 9
#| out.width: '100%'
#| fig.align: "center"

p_multiv_comp_sex_item
```

#### Checking for multivariate outliers

```{r check_outliers_item_scores}
performance::check_outliers(
  capl_res |> dplyr::select(
    pacer_score, 
    plank_score, 
    camsa_score,
    step_score, 
    self_report_pa_score,
    predilection_score, 
    adequacy_score,
    intrinsic_motivation_score,
    pa_competence_score, 
    pa_guideline_score, 
    crf_means_score,
    ms_means_score, 
    sports_skill_score,  
    fill_in_the_blanks_score
    ) |> 
    tidyr::drop_na(), 
  method = "mahalanobis_robust") # too many variables to use MCD method; alternative method chosen based on DOI: 10.3758/s13428-024-02356-w
```

#### R output for global comparison

The comparison of the multivariate distributions of item scores between girls and boys has been performed using non-parametric analysis implemented in functions from the `{npmv}` package.

##### Raw output

```{r item_global_multicomp_sex}
item_global_multicomp_sex
```

##### Formated output

```{r item_global_multicomp_sex_rel_eff}
item_global_multicomp_sex_rel_eff |>
  flextable() |>
  bold(i = 1, part = "header") |>
  bold( ~ `Rel. Eff. Girls` > 0.5, 4) |>
  bold( ~ `Rel. Eff. Boys` > 0.5, 5) |>
  bg( ~ `Rel. Eff. Girls` > 0.5, 4, bg = "grey90") |>
  bg( ~ `Rel. Eff. Boys` > 0.5, 5, bg = "grey90") |>
  width(j = 1, width = 2.5) |>
  width(j = 2, width = 1.5) |>
  width(j = 3, width = 1.5) |>
  valign(
    i = 1,
    j = 1:5,
    valign = "top",
    part = "header"
  ) |>
  align(j = 4:5, part = "header", align = "center") |>
  align(j = 4:5, part = "body", align = "center") |>
  add_footer_lines(
    "Min./ Max. Theo. Rel. Eff. = Minimum/maximum theoretical relative effect. A relative effect can be only between 0 and 1 and depicts the probability, for an individual randomly sampled from the considered group, to have a higher value than the one from an individual randomly sampled from both groups (girls and boys). Minimum and maximum theoretical relative effects are respectively the lowest and highest effect sizes than could be expected for a given group and score based on the number of girls and boys available for the considered score. Grey cells with bold values highlight the highest relative effects among girls and boys."
  )
```

:::{.callout-note}
The global analysis, based on the ANOVA type test p-value, suggests that girls and boys come from two different multivariate distributions related to the CAPL-2 item scores. The `$twogroupreleffects` section of the R output shows the probability, for a given  variable, that a girl or a boy randomly sampled respectively from girls or boys has a higher value than the one associated to a participant randomly sampled from both the girls and boys.
:::

#### R output for local comparisons

##### Raw output

```{r item_local_multicomp_sex}
cat(item_local_multicomp_sex, sep = "\n")
```

##### Graphical output

```{r item_local_multicomp_sex_graph}
#| column: screen
#| out-width: '100%'
#| out-height: '100%'
#| fig-height: 50
#| fig-width : 60

item_local_multicomp_sex_graph
```

## Between-physical literacy profile comparisons of movement behaviours

This part includes two subsections: a section showing the comparisons of the multivariate distributions of movement behaviour metrics between the physical literacy profiles; and a section showing the comparisons of the pattern of movement behaviours across the week between the physical literacy profiles. These analyses are based on data from participants having at least 4 valid days for the accelerometer-based measurement of movement behaviours and who had a valid CAPL-2 profile.

### Data skimming

#### Raw data

Navigation in the raw data (CAPL-2 scores along with movement behaviour metrics) is possible through the interactive table shown below. 

```{r capl_res_4_valid_days}
rmarkdown::paged_table(capl_res_4_valid_days)
```

#### Variable summaries

This section proposes an overview of the study dataset related to both the valid CAPL-2 profiles and the movement behaviour metrics in the participants with at least 4 valid days for the accelerometer-based measurement of movement behaviours. More precisely, the tables display information about the dataset structure as well as descriptive statistics for all the variables from the dataset. The interest of this section is mainly to verify that all the variables have been correctly formated and to have information about potential missing values.

```{r skim_pa_data_all_metrics}
skimr::skim(capl_res_4_valid_days)
```

### Distributions of the movement behaviour metrics

This section shows the distributions of the movement behaviour metrics that were deemed of potential interest for exploratory analysis. These metrics were directly available from the {activAnalyzer} package. Some metrics have been removed from the initial list of the available metrics. MPA and VPA minutes and related percentages of wear time have been removed because we had no tresholds to make a distinction between moderate and vigorous physical activity in children. Total kilocalories, physical activity level, and MVPA MET-hours have been removed because they were not based on children-specific equations (no appropriate equations were available in the {activAnalyzer} package) and there was also no consideration for these metrics that are usually poorly estimated. The retained metrics represent different movement behaviour concepts: activity volume, step accumulation, intensity distribution, and sedentary time accumulation pattern. Details about what the metrics mean are available in the manual of the {activAnalyzer} package. Of note, in the figure below, the list of the metrics that goes from `Wear time (min)` to `Number of breaks` represent daily means while the remaining metrics were computed considering the whole set of valid days of measurement.

```{r p_distri_all_metrics}
#| out-width: '100%'
#| fig-width: 15
#| fig-height: 17

p_distri_all_metrics
```

### Vizualisation of the (un)correlated movement behaviour variables based on Principal Component Analysis

As there were a lot of variables available to characterize movement behaviours, we conducted a principal component analysis (PCA) to evaluate to what extent the initial set of variables could be reduced. The rationale for variable selection was to have at least one variable for each of the movement behaviour concepts presented above while keeping the variables that were not perfectly or not too strongly correlated (strongly correlated variables could be observed on a PCA biplot with arrows that would point to the same direction or to opposite directions). For the variables related to activity volume, only the vector magnitude counts/min, the percentages of wear time spent sedentary or in light/moderate-to-vigorous physical activity, the step count and the MVPA / SED ratio were considered during PCA.

```{r p_biplot_metrics}
p_biplot_metrics
```

:::{.callout-note}
Based on the PCA biplot, we kept for further analysis: 

* For activity volume metrics: 
  + `vm_perm_min`
  + `percent_SED`
  + `percent_LPA`
  + `percent_MVPA`
  + `total_steps`

* For step accumulation metrics:
    + `max_steps_60min`
    + `peak_steps_60min`

* For intensity distribution metrics:
  + `ig`

* For sedentary behaviour accumulation metrics:
  + `mean_breaks`
  + `UBD`
  + `gini`
:::

### Checking of the correlations between the retained variables

```{r check_cor_metrics}
check_cor_metrics
```

:::{.callout-note}
Based on the correlation results, we finally removed `vm_perm_min`, `percent_LPA`, `peak_steps_60min` and `gini` to keep variables with lower correlations. The final list of the retained metrics is the following: 

* For activity volume metrics: 
  + `percent_SED`
  + `percent_MVPA`
  + `total_steps`

* For step accumulation metrics:
    + `max_steps_60min`

* For intensity distribution metrics:
  + `ig`

* For sedentary behaviour accumulation metrics:
  + `mean_breaks`
  + `UBD`
:::

### Checking for multivariate outliers

```{r check_outliers_pa_metrics}
performance::check_outliers(
  capl_res_4_valid_days |>
    dplyr::select(tidyselect::any_of(selected_metrics$raw_names)),
  method = "mahalanobis_robust") # too many variables to use MCD method; alternative method chosen based on DOI: 10.3758/s13428-024-02356-w
```

### Non-parametric multivariate analysis

#### Graphical analysis

```{r p_distri_all_metrics_by_profile}
#| out-width: '100%'
#| fig-width: 10
#| fig-height: 10

p_distri_all_metrics_by_profile
```

#### Tabular view

```{r tbl_retained_metrics}
tbl_retained_metrics |>
  gtsummary::as_flex_table()
```


#### Checking sex distribution across physical literacy profiles

We check that girls and boys were approximately equally distributed across the physical literacy profiles so that potential differences bewteen the profiles are not confounded by sex differences.

```{r counts_sex_by_capl_profile}
tar_read(capl_res_4_valid_days) |> 
  dplyr::count(capl_interpretation, gender) |>
  tidyr::pivot_wider(names_from = gender, values_from = n)
```

:::{.callout-note}
The distribution of girls and boys was quite balanced across the physical literacy profiles.
:::

#### R output for global comparison

The comparisons of the multivariate distributions of movement behaviour metrics between physical literacy profiles have been performed using non-parametric analysis implemented in functions from the `{npmv}` package.

##### Raw output

```{r metrics_global_multicomp_profile}
metrics_global_multicomp_profile
```

##### Formated output

```{r metrics_global_multicomp_profile_rel_eff}
metrics_global_multicomp_profile_rel_eff |>
  flextable() |>
  bold(i = 1, part = "header") |>
  bold( ~ `Rel. Eff. Beginning` > 0.5, 6) |>
  bold( ~ `Rel. Eff. Progressing` > 0.5, 7) |>
  bold( ~ `Rel. Eff. Achieving` > 0.5, 8) |>
  bold( ~ `Rel. Eff. Excelling` > 0.5, 9) |>
  bg( ~ `Rel. Eff. Beginning` > 0.5, 6, bg = "grey90") |>
  bg( ~ `Rel. Eff. Progressing` > 0.5, 7, bg = "grey90") |>
  bg( ~ `Rel. Eff. Achieving` > 0.5, 8, bg = "grey90") |>
  bg( ~ `Rel. Eff. Excelling` > 0.5, 9, bg = "grey90") |>
  width(j = 1, width = 2.5) |>
  width(j = 2:9, width = 1.3) |>
  valign(
    i = 1,
    j = 1:9,
    valign = "top",
    part = "header"
  ) |>
  align(j = 6:9, part = "header", align = "center") |>
  align(j = 6:9, part = "body", align = "center") |>
  add_footer_lines(
    "Min./ Max. Theo. Rel. Eff. = Minimum/maximum theoretical relative effect. A relative effect can be only between 0 and 1 and depicts the probability, for an individual randomly sampled from the considered group, to have a higher value than the one from an individual randomly sampled from all groups (all physical literacy profiles). Minimum and maximum theoretical relative effects are respectively the lowest and highest effect sizes than could be expected for a given group and metric based on the number of participants available for the considered metric. Grey cells with bold values highlight the highest relative effects among the physical literacy profiles."
  )
```

:::{.callout-note}
The global analysis, based on the ANOVA type test p-value, suggests that the physical literacy profiles come from different multivariate distributions related to movement behaviour metrics. The `$twogroupreleffects` section of the R output shows the probability, for a given  variable, that a participant randomly sampled from a given physical literacy profile has a higher value than the one associated to a participant randomly sampled from all physical literacy profiles together.
:::

#### R output for local comparisons

##### Raw output

```{r metrics_local_multicomp_profile}
cat(metrics_local_multicomp_profile, sep = "\n")
```

##### Graphical output

```{r metrics_local_multicomp_profile_graph}
#| out-width: '100%'
#| fig-width: 15
#| fig-height: 15
metrics_local_multicomp_profile_graph
```


