---
title: "Physical Literacy Profiles and Movement Behaviours in children: an exploratory study from the 'EPLPA' Project"
authors:
  - name: Henri Moncanis
    affiliation: 
      - ref: ifepsa_etud
    corresponding: false
  - name: Pierre-Yves de Müllenheim
    orcid: 0000-0001-9157-7371
    affiliation: 
      - ref: ifepsa_pro
    email: pydemull@uco.fr
    corresponding: false
  - name: Nicolas Hauw
    affiliation: 
      - ref: ifepsa_pro
    country: France
    email: nhauw@uco.fr
    corresponding: true
affiliations:
  - id: ifepsa_etud
    name: UCO-IFEPSA | Student
    city: Les Ponts-de-Cé
    country: France
  - id: ifepsa_pro
    name: UCO-IFEPSA | APCoSS
    city: Les Ponts-de-Cé
    country: France
date: today
date-format: "long"
format:
  html:
    embed-resources: true
    code-fold: true
    theme: cosmo
    toc: true
    toc-depth: 7
    toc-location: right
    number-depth: 7
    number-sections: true
    self-contained: true
    css: styles.css
title-block-banner: true
execute: 
  warning: false
  freeze: true
editor: source
---

```{r load_packages_and_targets}
#| echo: false

# Packages
library(flextable)
library(ggplot2)
library(targets)

# Targets
tar_load(tab_percents_num_valid_days)
tar_load(capl_res)
tar_load(p_capl_all_domains)
tar_load(desc_stats_capl_all)
tar_load(p_interpretation)
tar_load(p_capl_all_domains_by_sex)
tar_load(desc_stats_capl_by_sex)
tar_load(p_interpretation_by_sex)
tar_load(pa_data)
tar_load(tab_pa_metrics_config)
tar_load(capl_comp_sex)
tar_load(p_multiv_comp_sex_dom)
tar_load(domain_global_multicomp_sex)
tar_load(domain_local_multicomp_sex)
tar_load(p_multiv_comp_sex_item)
tar_load(item_global_multicomp_sex)
tar_load(item_local_multicomp_sex)
tar_load(capl_res_3_valid_days)
tar_load(p_counts_valid_ids_by_day)
tar_load(p_minutes_mvpa_by_day)
tar_load(p_percent_mvpa_by_day)
tar_load(df_3_valid_days)
tar_load(p_distri_all_metrics)
tar_load(biplot_metrics)
```

:::{.callout-note}
This document includes the results of the analytical pipeline of the project. If you want to look at the code that has been implemented to get the results, please see the `target.R` file and the `R/` folder associated to the present work.
:::

## Pre-analysis information

The CAPL-2 scores are partly based on a measurement of weekly steps. In the present study, this measurement was performed using a wGT3X-BT accelerometer (ActiGraph). The settings that have been used to process the accelerometer data files are shown in the table below. The `EPOCH_TARGET_CHILD` setting (epoch duration with which counts have been accumulated) is in seconds. The cut-points settings (intensity thresholds to perform intensity classification) are in counts/min. The `FRAME` settings (to detect nonwear time) are in minutes. The `MINIMUM_WEAR_TIME` setting (to consider a day as valid for further analysis) is in hours.

```{r show_pa_metrics_config}
rmarkdown::paged_table(tab_pa_metrics_config, options = list(rows.print = 11))
```

Of note, the package used to compute CAPL-2 scores (i.e., `{capl}`) required at least 4 valid days to compute a daily mean step count used for further analysis. If only 3 valid days were available, a step count for a fourth valid day was obtained by randomly sampling a step count among the available valid daily step counts (action performed by the package `{capl}`). No computation was performed when less than 3 valid days were available.

For a better understanding of the results, the table below shows the percentages of participants by number of valid days for the measurement of usual movement behaviours.

```{r tab_percents_num_valid_days}
#| ft.align: "center"

tab_percents_num_valid_days
```

## Global descriptive analysis of the CAPL-2 scores

### Data skimming

#### Raw data

Navigation in the raw data is possible through the interactive table shown below. 

```{r show_capl_database}
rmarkdown::paged_table(capl_res)
```

#### Variable summaries

This section proposes an overview of the final study dataset related to the CAPL-2 scores. Below the tables display information about the dataset structure as well as descriptive statistics for all the variables from the dataset.

```{r skim_capl_res}
skimr::skim(capl_res)
```

### Score distributions

#### Graphical view

```{r show_capl_scores}
#| fig.height: 15
#| fig.width: 12
#| out.width: '100%'
#| fig.align: "center"

p_capl_all_domains
```

#### Tabular view

```{r desc_stats_capl_all}
desc_stats_capl_all |>
  italic(i = 1, j = 2, part = "header") |>
  bold(i = c(1, 5, 8, 13, 19), j = 1:3)
```

### Interpretation category distributions

```{r show_interpretations}
#| fig.height: 7
#| fig.width: 9
#| out.width: '100%'
#| fig.align: "center"

p_interpretation
```

## Between-sex comparisons of CAPL-2 scores

### Score distributions

#### Graphical view

```{r show_capl_scores_by_sex}
#| fig.height: 16
#| fig.width: 13
#| out.width: '100%'
#| fig.align: "center"

p_capl_all_domains_by_sex
```

#### Tabular view

```{r desc_stats_capl_by_sex}
desc_stats_capl_by_sex |>
  italic(i = 1, j = 2, part = "header") |> 
  bold(i = c(1, 5, 8, 13, 19), j = 1:4)
  
```

### Interpretation category distributions

```{r show_interpretations_by_sex}
#| fig.height: 7
#| fig.width: 9
#| out.width: '100%'
#| fig.align: "center"

p_interpretation_by_sex
```

### Comparison of CAPL-2 global scores

```{r capl_comp_sex}
capl_comp_sex
```

### Comparison of CAPL-2 domain scores

#### Graphical analysis

```{r p_multiv_comp_sex_dom}
#| fig.height: 4
#| fig.width: 9
#| out.width: '100%'
#| fig.align: "center"

p_multiv_comp_sex_dom
```

#### Non-parametric multivariate analysis

##### R output for global comparison

```{r domain_global_multicomp_sex}
domain_global_multicomp_sex
```

##### R output for local comparisons

```{r domain_local_multicomp_sex}
cat(domain_local_multicomp_sex, sep = "\n")
```

### Comparison of CAPL-2 item scores

#### Graphical analysis

```{r p_multiv_comp_sex_item}
#| fig.height: 7
#| fig.width: 12
#| out.width: '100%'
#| fig.align: "center"

p_multiv_comp_sex_item
```


#### R output for global comparison

```{r item_global_multicomp_sex}
item_global_multicomp_sex
```

#### R output for local comparisons

```{r item_local_multicomp_sex}
cat(item_local_multicomp_sex, sep = "\n")
```

## Comparisons of the physical literacy profiles regarding the movement behaviour metrics

The following analyses are based on participants with at least 3 valid days for the accelerometer-based measurement of movement behaviours.

### Comparisons of the movement behaviour metrics

#### Data skimming

##### Raw data

Navigation in the raw data (CAP-2 scores along with daily means of movement behaviour metrics) is possible through the interactive table shown below. 

```{r capl_res_3_valid_days}
rmarkdown::paged_table(capl_res_3_valid_days)
```

##### Variable summaries

This section proposes an overview of the study dataset related to both the CAPL-2 profiles and the movement behaviour metrics in participants with at least 3 valid days for the accelerometer measurement. Below the tables display information about the dataset structure as well as descriptive statistics for all the variables from the dataset.

```{r skim_pa_data_all_metrics}
skimr::skim(capl_res_3_valid_days)
```

#### Distributions of the movement behaviour metrics

```{r p_distri_all_metrics}
#| out-width: '100%'
#| fig-width: 15
#| fig-height: 17

p_distri_all_metrics
```

#### Vizualisation of the (un)correlated movement behaviour variables based on Principal Component Analysis

```{r biplot_metrics}
biplot_metrics
```

:::{.callout-note}
Based on the PCA biplot, we keep for further analysis: 

* For activity volume metrics: 

**`vm_per_min`
**`percent_SED`
**`percent_LPA`
**`percent_MVPA`
**`ratio_mvpa_sed`
**`total_steps`

* For step-based metrics:

**`max_steps_60min`
**`peak_steps_60min`

* For intensity distribution metrics:

**`ig`

* For sedentary behaviour accumulation metrics:

**`mean_breaks`
**`MBD`
**`gini`
:::

### Comparisons of week trajectories of movement behaviour metrics across the physical literacy profiles

#### Wear time analysis

```{r p_counts_valid_ids_by_day}
p_counts_valid_ids_by_day
```

:::{.callout-note}
The total number of students is not the same for all the days of the week since the students actually did not complete 7 full days of measurement but 6 (for practical reasons).
:::

#### Visualize MVPA minutes by day

```{r p_minutes_mvpa_by_day}
p_minutes_mvpa_by_day
```

#### Visualize MVPA % of wear time

```{r p_percent_mvpa_by_day}
p_percent_mvpa_by_day
```

### Model based on MVPA % of wear time
```{r}
#| fig-width: 12
#| fig-height: 12

# Build model
mod <- lmerTest::lmer(
  percent_MVPA ~ day * capl_interpretation + (1 | id), 
  data = df_3_valid_days |> 
    dplyr::filter(validity == "valid" & capl_interpretation != "Non available") |> 
    dplyr::mutate(capl_interpretation = factor(capl_interpretation, levels = c("Beginning", "Progressing", "Achieving", "Excelling"))))

# Check model summary
summary(mod)

# Check model quality
performance::check_model(mod)
```


## Export datasets

```{r}
# Export CAPL results
readr::write_csv2(capl_res, "out/capl_res.csv")
```

