---
title: "EPLPA Project"
authors:
  - name: Henri Moncanis
    affiliation: 
      - ref: ifepsa_etud
    corresponding: false
  - name: Pierre-Yves de Müllenheim
    orcid: 0000-0001-9157-7371
    affiliation: 
      - ref: ifepsa_pro
    email: pydemull@uco.fr
    corresponding: false
  - name: Nicolas Hauw
    affiliation: 
      - ref: ifepsa_pro
    country: France
    email: nhauw@uco.fr
    corresponding: true
affiliations:
  - id: ifepsa_etud
    name: UCO-IFEPSA | Student
    city: Les Ponts-de-Cé
    country: France
  - id: ifepsa_pro
    name: UCO-IFEPSA | APCoSS
    city: Les Ponts-de-Cé
    country: France
date: today
date-format: "long"
format:
  html:
    embed-resources: true
    code-fold: true
    theme: cosmo
    toc: true
    toc-depth: 5
    toc-location: right
    number-depth: 5
    number-sections: true
    self-contained: true
    css: styles.css
title-block-banner: true
execute: 
  warning: false
  freeze: true
editor: source
---

```{r load_packages_and_targets}
#| echo: false

# Packages
library(flextable)
library(ggplot2)
library(targets)

# Targets
tar_load(capl_res)
tar_load(p_capl_all_domains)
tar_load(desc_stats_capl_all)
tar_load(p_interpretation)
tar_load(p_capl_all_domains_by_sex)
tar_load(desc_stats_capl_by_sex)
tar_load(p_interpretation_by_sex)
tar_load(pa_data)
tar_load(tab_pa_metrics_config)
tar_load(p_multiv_comp_sex)
tar_load(capl_comp_sex)
tar_load(tab_percents_num_valid_days)
tar_load(p_counts_valid_ids_by_day)
tar_load(p_minutes_mvpa_by_day)
tar_load(p_percent_mvpa_by_day)
```

## Accelerometer data analysis settings

The settings that have been used to process the accelerometer data files are shown in the table below. The `EPOCH_TARGET_CHILD` setting is in seconds. The cut-points settings are in counts/min. The `FRAME` settings are in minutes (these last settings were used to detect nonwear time). The `MINIMUM_WEAR_TIME` setting is in hours.

```{r show_pa_metrics_config}
rmarkdown::paged_table(tab_pa_metrics_config, options = list(rows.print = 11))
```

## CAPL-2 score analysis

### Data skimming

#### Raw data

Navigation in the raw data is possible through the interactive table shown below. 

```{r show_capl_database}
rmarkdown::paged_table(capl_res)
```

#### Variable summaries

This section proposes an overview of the final study dataset. Below the tables display information about the dataset structure as well as descriptive statistics for all the variables from the dataset.

```{r skim_capl_res}
skimr::skim(capl_res)
```

### Score and interpretation categories distributions

#### Whole group of students

##### Scores

###### Graphical view

```{r show_capl_scores}
#| fig.height: 15
#| fig.width: 12
#| out.width: '100%'
#| fig.align: "center"

p_capl_all_domains
```

###### Tabular view

```{r desc_stats_capl_all}
desc_stats_capl_all |>
  italic(i = 1, j = 2, part = "header") |>
  bold(i = c(1, 5, 8, 13, 19), j = 1:3)
```

##### Interpretation categories

```{r show_interpretations}
#| fig.height: 7
#| fig.width: 9
#| out.width: '100%'
#| fig.align: "center"

p_interpretation
```

#### By sex

##### Scores

###### Graphical view

```{r show_capl_scores_by_sex}
#| fig.height: 16
#| fig.width: 13
#| out.width: '100%'
#| fig.align: "center"

p_capl_all_domains_by_sex
```

###### Tabular view

```{r desc_stats_capl_by_sex}
desc_stats_capl_by_sex |>
  italic(i = 1, j = 2, part = "header") |> 
  bold(i = c(1, 5, 8, 13, 19), j = 1:4)
  
```

##### Interpretation categories

```{r show_interpretations_by_sex}
#| fig.height: 7
#| fig.width: 9
#| out.width: '100%'
#| fig.align: "center"

p_interpretation_by_sex
```

##### Between-sex score comparisons

###### Visualize multivariate distributions

```{r p_multiv_comp_sex}
p_multiv_comp_sex
```

###### Compare CAPL-2 scores

```{r capl_comp_sex}
capl_comp_sex
```

###### Compare physical literacy domain scores

```{r domain_local_multicomp_sex}
npmv::ssnonpartest(
  pc_score | db_score | mc_score | ku_score ~ gender,
  data = capl_res,
  test = c(1, 0, 0, 0),
  alpha = 0.05,
  factors.and.variables = TRUE
)
```

###### Compare physical literacy item scores

```{r item_local_multicomp_sex}
npmv::ssnonpartest(
      step_score	| self_report_pa_score |
        predilection_score | adequacy_score | intrinsic_motivation_score |
        pa_competence_score | pa_guideline_score | crf_means_score |
        ms_means_score | sports_skill_score | fill_in_the_blanks_score ~ gender,
      data = capl_res,
      test = c(1, 0, 0, 0),
      alpha = 0.05,
      factors.and.variables = TRUE
    )
```

## Trajectories of MVPA across the week

### Data skimming

#### Raw data

Navigation in the raw data (metric daily summaries) is possible through the interactive table shown below. 

```{r show_pa_database}
pa_data$all_metrics$id <- as.factor(pa_data$all_metrics$id)
rmarkdown::paged_table(pa_data$all_metrics)
```

#### Variable summaries

```{r skim_pa_data_all_metrics}
skimr::skim(pa_data$all_metrics)
```

### Wear time analysis

#### Rates of participants per number of valid days

```{r tab_percents_num_valid_days}
tab_percents_num_valid_days
```

#### Counts of students with valid data across the week among those having 3 valid days or more

```{r p_counts_valid_ids_by_day}
p_counts_valid_ids_by_day
```

### Physical activity profile

#### MVPA minutes

```{r p_minutes_mvpa_by_day}
p_minutes_mvpa_by_day
```

#### MVPA % of wear time

```{r p_percent_mvpa_by_day}
p_percent_mvpa_by_day
```

## Export datasets

```{r}
# Export CAPL results
readr::write_csv2(capl_res, "out/capl_res.csv")
```

